Yield Mapping

### 2016-02-28 Rmd/biodiversity-layer.Rmd
Supplementary methods draft complete. Required changes to biodiversity-layer.Rmd. Fixed bug in Figure 4 for main text--wrong map selected.

## Prepare impacts layer
```{r, eval = FALSE}
vnms <- dir(full_path(p_bd, "act_veg"), pattern = ".tif$")
vnms <- vnms[vnms != "veg88.tif"]  # drop water bodies
fnms <- full_path(full_path(p_bd, "act_veg"), vnms)
s <- stack(lapply(fnms, function(x) raster(x)))
sm <- mask(s, mgrid)

# keep for assessing impacts
writeRaster(sm, filename = full_path(p_bd, "ZA-vegremain.tif"), 
            overwrite = TRUE)
vegnames <- gsub("\\.tif", "", gsub("veg", "v", vnms))
save(vegnames, file = full_path(p_bd, "ZA-vegremain.rda"))

# Sum for total - the inverse of this will be the farmable areas
remfrac <- calc(s, sum)
remfrac <- mask(remfrac, mgrid)
writeRaster(remfrac, filename = full_path(p_bd, "ZA-remfrac.tif"), 
            overwrite = TRUE)

# Calculate intactness
w <- matrix(nrow = 11, ncol = 11)
w[] <- 1
intact <- focal(remfrac, w = w, fun = mean, na.rm = TRUE)
writeRaster(intact, filename = full_path(p_bd, "intactness.tif"), 
            overwrite = TRUE)

# intact <- mask(intact, mgrid)
# plot(intact)

# Calculate a veg type weight based on relative remaining area
veg_dt <- dtraster::as.data.table(sm)  # stack and convert to dt
veg_dt <- na.omit(veg_dt)
vnms <- names(veg_dt)[-c(1:2)]
vtots <- veg_dt[, lapply(.SD, function(x) sum(x * 100)), 
                .SDcols = vnms]  
wgti <- round(1 / (vtots / nrow(veg_dt)), 2)  # bd weights (1 = rarest)
# wgt <- round(vtots / nrow(veg_dt), 4)  # biodiversity weights (1 = most common)
# plot(unlist(wgti), unlist(wgt))

@@

### Weighting in relation to rarity and protectedness
```{r, eval = FALSE}
# Combine protected areas (NPs and GMAs, forest reserves)
nps$code <- ifelse(nps$TYPE == "gma", 2, 1) 
npsr <- rasterize(nps, mgrid, field = "code")  # rasterize NPs/GMAs
npsr[is.na(npsr)] <- 0  
freserves$code <- 3  
freservesr <- rasterize(freserves, mgrid, field = "code")  # forest reserves
freservesr[is.na(freservesr)] <- 0
pas <- npsr + freservesr  # sum them
reclmat <- cbind(0:5, c(0:3, 1, 2))
pas <- reclassify(pas, reclmat)
pas <- mask(pas, mgrid)
writeRaster(pas, filename = full_path(p_bd, "ZA-pas.tif"))
# plot(pas)
# plot(freservesr)

# Let's look at how much veg is protected, and maybe use that as basis for 
# weights - rarity + proportion protected
smpa <- mask(stack(s, pas), mgrid)
vegpa_dt <- as.data.table(smpa)
vegpa_dt <- na.omit(vegpa_dt)
setnames(vegpa_dt, "layer", "PA")
protected <- vegpa_dt[, lapply(.SD, sum(x * 100)), by = PA, .SDcols = vnms]
protected <- cbind("PA" = protected[, PA], 
                   protected[, lapply(.SD, function(x) {
                       round(x / sum(x), 3)
                   }), .SDcols = vnms])
# proportion protected in both NPs and GMA, and just in NPs
prop_prot2 <- protected[PA %in% c(1:2), lapply(.SD, sum), .SDcols = vnms]
prop_prot1 <- protected[PA == 1, lapply(.SD, sum), .SDcols = vnms]  # nps only

# stack PAS with intact area
pasconvs <- mask(stack(pas, remfrac), mgrid)
pa_dt <- as.data.table(pasconvs)
pa_dt <- na.omit(pa_dt)
setnames(pa_dt, c("layer.1", "layer.2"), c("pas", "nveg"))
pa_dt[, (1 - sum(nveg) / .N) * 100 , by = "pas"]
pa_dt[, .N, by = "pas"]

@@

# plots to examine them
labs <- gsub("veg", "", names(wgtsn))
# par(mfrow = c(2, 1), mar = c(2, 2, 2, 2))
# weights against protected proportion (NPs + GMAs)
plot(wgtsn, prop_prot2, pch = "", ylab = "")
text(wgtsn, prop_prot2, labels = labs, cex = 0.75)
# weights against protected proportion (NPs only)
plot(wgtsn, prop_prot1, pch = "", ylab = "")
text(wgtsn, prop_prot1, labels = labs, cex = 0.75)
# additive weights factoring in protected proportion versus protected proportion
plot(wgts_prop, prop_prot2, pch = "", ylab = "")
text(wgts_prop,  prop_prot2, labels = labs, cex = 0.75)
# BD + NP protected proportion versus NP protected proportion
plot(wgts_prop_np, prop_prot1, pch = "", ylab = "")
text(wgts_prop_np,  prop_prot1, labels = labs, cex = 0.75)
# protected proportion weighted versus same but log-transformed
plot(wgts_prop, wgts_propl, pch = "", ylab = "")
text(wgts_prop,  wgts_propl, labels = labs, cex = 0.75)
# Bd weights against BD + protected proportion weights
plot(wgtsn, wgts_prop, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn, wgts_prop, labels = labs, cex = 0.75)
# Bd weights against BD + NP protected proportion weights
plot(wgtsn, wgts_prop_np, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn, wgts_prop_np, labels = labs, cex = 0.75)
# Bd weights versus log-transformed BD + protected proportion weights
plot(wgtsn, wgts_propl, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn,  wgts_propl, labels = labs, cex = 0.75)
# The same but against multiplicative weights
plot(wgtsn, wgtsn * unlist(1 - prop_prot1), pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn,  wgtsn * unlist(1 - prop_prot1), labels = labs, cex = 0.75)
# sort(wgts_prop); sort(wgts_prop_np)
# sort(wgtsn)

@@

writeRaster(bdf, file = full_path(p_bd, "cons-priorities.tif"), 
            overwrite = TRUE)
bdprops <- cbind("var" = c("area", "rarity", "priority"),
                 rbind(vtots / nrow(veg_dt), data.table(t(wgtsn)), 
                       data.table(t(wgts_prop_np))))
names(bdprops) <- gsub("veg", "v", names(bdprops))
save(bdprops, file = full_path(p_bd, "ZA-bdprops.rda"))
# load(full_path(p_bd, "ZA-bdprops.rda"))

>>>>

## Prepare impacts layer
```{r, eval = FALSE}
vnms <- dir(full_path(p_bd, "act_veg"), pattern = ".tif$")
vnms <- vnms[vnms != "veg88.tif"]  # drop water bodies
fnms <- full_path(full_path(p_bd, "act_veg"), vnms)
s <- stack(lapply(fnms, function(x) raster(x)))
# sm <- raster::mask(s, mgrid)

# keep for assessing impacts
# writeRaster(sm, filename = full_path(p_bd, "ZA-vegremain.tif"), 
#             overwrite = TRUE)
sm <- brick(full_path(p_bd, "ZA-vegremain.tif"))
vegnames <- gsub("\\.tif", "", gsub("veg", "v", vnms))
save(vegnames, file = full_path(p_bd, "ZA-vegremain.rda"))
names(sm) <- vegnames

# Sum for total - the inverse of this will be the farmable areas
# remfrac <- calc(s, sum)
# remfrac <- mask(remfrac, mgrid)
# writeRaster(remfrac, filename = full_path(p_bd, "ZA-remfrac.tif"), 
#             overwrite = TRUE)
remfrac <- raster(full_path(p_bd, "ZA-remfrac.tif"))

# Calculate intactness
# w <- matrix(nrow = 11, ncol = 11)
# w[] <- 1
# intact <- focal(remfrac, w = w, fun = mean, na.rm = TRUE)
# writeRaster(intact, filename = full_path(p_bd, "intactness.tif"), 
#             overwrite = TRUE)
intact <- raster(full_path(p_bd, "intactness.tif"))
intact <- raster::mask(intact, mgrid)
# plot(intact)

# Calculate a veg type weight based on relative remaining area
veg_dt <- dtraster::as.data.table(sm)  # stack and convert to dt
veg_dt <- na.omit(veg_dt)
vnms <- names(veg_dt)[-c(1:2)]
vtots <- veg_dt[, lapply(.SD, function(x) sum(x * 100)), 
                .SDcols = vnms]  
wgti <- round(1 / (vtots / nrow(veg_dt)), 2)  # bd weights (1 = rarest)
wgts <- round((vtots / 100) / nrow(veg_dt), 4)  # veg prop (1 = most common)
# plot(unlist(wgti), unlist(wgt))

@@

### Weighting in relation to rarity and protectedness
```{r, eval = FALSE}
# Combine protected areas (NPs and GMAs, forest reserves)
# nps$code <- ifelse(nps$TYPE == "gma", 2, 1) 
# npsr <- rasterize(nps, mgrid, field = "code")  # rasterize NPs/GMAs
# npsr[is.na(npsr)] <- 0  
# freserves$code <- 3  
# freservesr <- rasterize(freserves, mgrid, field = "code")  # forest reserves
# freservesr[is.na(freservesr)] <- 0
# pas <- npsr + freservesr  # sum them
# reclmat <- cbind(0:5, c(0:3, 1, 2))
# pas <- reclassify(pas, reclmat)
# pas <- mask(pas, mgrid)
# writeRaster(pas, filename = full_path(p_bd, "ZA-pas.tif"))
pas <- raster(full_path(p_bd, "ZA-pas.tif"))
# plot(pas)
# plot(freservesr)

# Let's look at how much veg is protected, and use that as basis for 
# weights - rarity + proportion protected
names(s) <- vnms
smpa <- raster::mask(stack(s, pas), mgrid)
vegpa_dt <- as.data.table(smpa)
vegpa_dt <- na.omit(vegpa_dt)
setnames(vegpa_dt, "ZA.pas", "PA")
protected <- vegpa_dt[, lapply(.SD, sum(x * 100)), by = PA, .SDcols = vnms]
protected <- cbind("PA" = protected[, PA], 
                   protected[, lapply(.SD, function(x) {
                       round(x / sum(x), 3)
                   }), .SDcols = vnms])
# proportion protected in both NPs and GMA, and just in NPs
prop_prot2 <- protected[PA %in% c(1:2), lapply(.SD, sum), .SDcols = vnms]
prop_prot1 <- protected[PA == 1, lapply(.SD, sum), .SDcols = vnms]  # nps only

# stack PAS with intact area
pasconvs <- raster::mask(stack(pas, remfrac), mgrid)
pa_dt <- as.data.table(pasconvs)
pa_dt <- na.omit(pa_dt)
setnames(pa_dt, c("ZA.pas", "ZA.remfrac"), c("pas", "nveg"))
pa_dt[, (1 - sum(nveg) / .N) * 100 , by = "pas"]
pa_dt[, .N, by = "pas"]

@@

# save vegetation stats
vegstats <- rbind(cbind("PA" = NA, wgts), protected)
save(vegstats, file = fp(p_bd, "vegstats.rda"))

# plots to examine them
labs <- gsub("v", "", names(wgtsn))
# par(mfrow = c(2, 1), mar = c(2, 2, 2, 2))
# weights against protected proportion (NPs + GMAs)
plot(wgtsn, prop_prot2, pch = "", ylab = "")
text(wgtsn, prop_prot2, labels = labs, cex = 0.75)
# weights against protected proportion (NPs only)
plot(wgtsn, prop_prot1, pch = "", ylab = "")
text(wgtsn, prop_prot1, labels = labs, cex = 0.75)
# additive weights factoring in protected proportion versus protected proportion
plot(wgts_prop, prop_prot2, pch = "", ylab = "")
text(wgts_prop,  prop_prot2, labels = labs, cex = 0.75)
# BD + NP protected proportion versus NP protected proportion
plot(wgts_prop_np, prop_prot1, pch = "", ylab = "")
text(wgts_prop_np,  prop_prot1, labels = labs, cex = 0.75)
# protected proportion weighted versus same but log-transformed
plot(wgts_prop, wgts_propl, pch = "", ylab = "")
text(wgts_prop,  wgts_propl, labels = labs, cex = 0.75)
# Bd weights against BD + protected proportion weights
plot(wgtsn, wgts_prop, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn, wgts_prop, labels = labs, cex = 0.75)
# Bd weights against BD + NP protected proportion weights
plot(wgtsn, wgts_prop_np, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn, wgts_prop_np, labels = labs, cex = 0.75)
# Bd weights versus log-transformed BD + protected proportion weights
plot(wgtsn, wgts_propl, pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn,  wgts_propl, labels = labs, cex = 0.75)
# The same but against multiplicative weights
plot(wgtsn, wgtsn * unlist(1 - prop_prot1), pch = "", ylab = "")
lines(c(0, 1), c(0, 1))
text(wgtsn,  wgtsn * unlist(1 - prop_prot1), labels = labs, cex = 0.75)
# sort(wgts_prop); sort(wgts_prop_np)
# sort(wgtsn)

@@

writeRaster(bdf, file = full_path(p_bd, "cons-priorities.tif"), 
            overwrite = TRUE)
bdprops <- cbind("var" = c("area", "rarity", "priority"),
                 rbind(vtots / nrow(veg_dt), data.table(t(wgtsn)), 
                       data.table(t(wgts_prop_np))))
names(bdprops) <- gsub("veg", "v", names(bdprops))
save(bdprops, file = full_path(p_bd, "ZA-bdprops.rda"))
# load(full_path(p_bd, "ZA-bdprops.rda"))
# bdprops
# bdprops[var == "area", rowSums(.SD), .SDcols = 2:ncol(bdprops)]
```

### 2016-02-28 Rmd/empirical-yields.Rmd
Supplementary methods draft complete. Required changes to biodiversity-layer.Rmd. Fixed bug in Figure 4 for main text--wrong map selected.

# gams to keep 
save(gam13, gam14, gam20, gam21, gam23, sgam7, sgam14, sgam15, sgam16, 
     file = fp(p_yield, "empirical/gams1.rda"))
# load(fp(p_yield, "empirical/gams1.rda"))
summary(gam13)
summary(sgam14)

@@

>>>>

# gams to keep 
save(gam13, gam14, gam20, gam21, gam23, sgam7, sgam14, sgam15, sgam16, 
     file = fp(p_yield, "empirical/gams1.rda"))
# load(fp(p_yield, "empirical/gams1.rda"))
```

@@

summary(gam20)
summary(sgam7)

### 2016-02-28 Rmd/figures.Rmd
Supplementary methods draft complete. Required changes to biodiversity-layer.Rmd. Fixed bug in Figure 4 for main text--wrong map selected.

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_other <- fp(p_root, "external/input_devel/other/")
# p_roads <- fp(p_root, "external/input_devel/roads")
# p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
#                    "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

@@

cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# sctab <- do.call(rbind, scens) * 100
cx <- 0.7
# lcols <- c("black", "red", "blue")
# imp_pct[, {
#   png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
#       units = "in", res = 300)
#   par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
#   plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
#   lines(conv_area, int_prior, col = "red")
#   lines(conv_area, mu_cost, col = "blue")
#   axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.2, mgp = c(1, 0.25, 0))
#   axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.15, mgp = c(1, 0.25, 0))
#   mtext("% land savings", side = 1, line = 1, cex = cx)
#   mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
#   inms <- c("tot_C", "int_prior", "mu_cost")
#   for(i in 1:length(inms)) {
#     text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
#          cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
#     text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
#          offset = i * 0.15 - 0.2, col = lcols[i])
#   }
#   legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
#          text.col = lcols, col = lcols, bty = "n", lty = 1)
imp_pct[, {
  png(fp(p_figures, "weight_impact3.png"), height = 4, width = 4, 
      units = "in", res = 300)
  plot(xwgts, conv_areap, type = "l", xlab = "", ylab = "", axes = FALSE, 
       ylim = c(0, 55), col = cols_tr[1])
  lines(xwgts, tot_Cp, col = cols_tr[2])
  lines(xwgts, int_priorp, col = cols_tr[3])
  lines(xwgts, mu_costp, col = cols_tr[4])
  axis(1, at = xwgts, labels = seq(0, 90, 10), cex = cx, cex.axis = cx, 
       line = -0.25, tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 55, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% Weight taken from Yield and divided", side = 1, line = 1, cex = cx)
  mtext("equally between Carbon & Biodiversity", side = 1, line = 1.75, 
        cex = cx)
  mtext("% Avoided Cost", side = 2, line = 1, cex = cx)
  legend("bottomright", 
         legend = c("Yield", "Carbon", "Biodiversity", "Travel time"), 
         cex = cx, text.col = cols_tr, col = cols_tr, bty = "n", lty = 1, 
         inset = c(0, 0.25, 0, 0))
  dev.off()
}]

@@

```{r, eval = FALSE}
# use minmax stats from optimal solution set
# pare <- ybdc$both$optitab
optirange <- pare[, lapply(.SD, range), .SDcols = 1:4]
optirange[1, lapply(.SD, function(x) x * 1.05)] - optirange[1, ]

@@

# select out those values from the results tables and grab conversion areas
parms <- round(ybdc$both$params[, 7:10], 2)
eqind <- which(apply(parms, 1, function(x) all(x == 0.25))) # iter of eq wt run
# pare[ind == eqind]

@@

# plot
png(fp(p_figures, "compromise_5pct.png"), height = 3.5, 
    width = 7, units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

@@

par(oma = c(0, 0, 0, 1))
# plot(zambia)
imp_plot2(toresr[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
          crops = "", ftitle = "Compromise equally", col = "purple", 
          legend = FALSE, hold = TRUE, stats = FALSE, cexscale = 0.4, 
          marg = c(0, 0, 1, 0), titline = 0)
legend("bottomright", legend = "Protected Areas", pch = 15, col = "grey75",
       bty = "n", pt.cex = 3 * 0.5, cex = 1.5 * 0.5, inset = c(0, 0.1, 0, 0))

@@

>>>>

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_other <- fp(p_root, "external/input_devel/other/")
p_bd <- fp(p_root, "external/input_devel/biodiversity")
# p_roads <- fp(p_root, "external/input_devel/roads")
# p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
#                    "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

@@

cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
# sctab <- do.call(rbind, scens) * 100
cx <- 0.7
# lcols <- c("black", "red", "blue")
# imp_pct[, {
#   png(fp(p_figures, "weight_impact.png"), height = 4, width = 4, 
#       units = "in", res = 300)
#   par(mgp = c(2, 0.75, 0), mar = c(3, 3, 1, 1))
#   plot(conv_area, tot_C, type = "l", xlab = "", ylab = "", #xaxt = "n", 
#   lines(conv_area, int_prior, col = "red")
#   lines(conv_area, mu_cost, col = "blue")
#   axis(1, at = seq(2, 12, 1), cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.2, mgp = c(1, 0.25, 0))
#   axis(2, at = seq(0, 60, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
#        tcl = -0.15, mgp = c(1, 0.25, 0))
#   mtext("% land savings", side = 1, line = 1, cex = cx)
#   mtext("% Carbon/Biodiv/Cost savings", side = 2, line = 1, cex = cx)
#   inms <- c("tot_C", "int_prior", "mu_cost")
#   for(i in 1:length(inms)) {
#     text(conv_area[-1], get(inms[i])[-1], labels = sctab[-1, i + 1], 
#          cex = cx * 0.8, pos = 3, offset = 0.2, col = lcols[i])
#     text(conv_area[1] + 0.1, i, labels = 0, cex = cx * 0.8, pos = 3, 
#          offset = i * 0.15 - 0.2, col = lcols[i])
#   }
#   legend("bottomleft", legend = c("Carbon", "Biodiv", "Cost"), cex = cx,
#          text.col = lcols, col = lcols, bty = "n", lty = 1)
imp_pct[, {
  png(fp(p_figures, "weight_impact4.png"), height = 4, width = 4, 
      units = "in", res = 300)
  plot(xwgts, conv_areap, type = "l", xlab = "", ylab = "", axes = FALSE, 
       ylim = c(0, 55), col = cols_tr[1])
  lines(xwgts, tot_Cp, col = cols_tr[2])
  lines(xwgts, int_priorp, col = cols_tr[3])
  lines(xwgts, mu_costp, col = cols_tr[4])
  axis(1, at = xwgts, labels = seq(0, 90, 10), cex = cx, cex.axis = cx, 
       line = -0.25, tcl = -0.2, mgp = c(1, 0.25, 0))
  axis(2, at = seq(0, 55, 5), las = 2, cex = cx, cex.axis = cx, line = -0.25, 
       tcl = -0.15, mgp = c(1, 0.25, 0))
  mtext("% Weight taken from Yield and divided", side = 1, line = 1, cex = cx)
  mtext("equally between Carbon & Biodiversity", side = 1, line = 1.75, 
        cex = cx)
  mtext("% Avoided Cost", side = 2, line = 1, cex = cx)
  legend("bottomright", 
         legend = c("Yield", "Carbon", "Biodiversity", "Travel time"), 
         cex = cx, text.col = cols_tr, col = cols_tr, bty = "n", lty = 1, 
         inset = c(0, 0.25, 0, 0))
  dev.off()
}]

@@

```{r, eval = FALSE}
# use minmax stats from optimal solution set
pare <- ybdc$both$optitab
optirange <- pare[, lapply(.SD, range), .SDcols = 1:4]
optirange[1, lapply(.SD, function(x) x * 1.05)] - optirange[1, ]

@@

# select out those values from the results tables and grab conversion areas
parms <- round(ybdc$both$params[, 7:10], 2)
eqind <- which(apply(parms, 1, function(x) all(x == 0.25))) # iter of eq wt run
parms[1031, ]
# pare[ind == eqind]

@@

# plot
png(fp(p_figures, "compromise_5pct2.png"), height = 3.5, 
    width = 7, units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

@@

par(oma = c(0, 0, 0, 1))
# plot(zambia)
imp_plot2(toresr$eqwt, impacts = i1, fpath = p_figures, fnm = "bob",
          crops = "", ftitle = "Compromise equally", col = "purple", 
          legend = FALSE, hold = TRUE, stats = FALSE, cexscale = 0.4, 
          marg = c(0, 0, 1, 0), titline = 0)
legend("bottomright", legend = "Protected Areas", pch = 15, col = "grey75",
       bty = "n", pt.cex = 3 * 0.5, cex = 1.5 * 0.5, inset = c(0, 0.1, 0, 0))

@@

# vegetation types
load(fp(p_bd, "vegstats.rda"))
vegstats <- round(vegstats * 100, 2)
nms <- c("Afromontane rain forest", "Zambezian dry evergreen forest", 
         "Zambezian dry deciduous forest", "Palm wooded grassland",
         "Riverine wooded vegetation", "Zambezian Kalahari woodland",
         "Drier miombo woodland", "Miombo woodland on hills/outcrops",
         "Wetter mimbo woodland", "N. Zambezian undifferentiated woodland",
         "Catena of N. Zambezian undifferentiated woodland/edaphic grassland", 
         "Mopane woodland/scrub woodland", "Zambezian chipya woodland",
         "Itigi thicket", "Swamp forest",
         "Edaphic grassland on drainage impeded/seasonally flooded soils", 
         "Bush groups, typically around termitaria",
         "Edaphic grassland w/Zambezian Kalahari woodland",
         "Edaphic grassland w/freshwater swamp", 
         "Edaphic woodland on drainage impeded/seasonally flooded soils")
print(xtable::xtable(cbind(c("", nms), unname(t(vegstats)[, c(1:2, 4, 3, 5)])), 
                           digits = c(2, 2, 2, 1, 1, 1, 1), ))

### 2016-02-28 Rmd/yield-predictors.rmd
Supplementary methods draft complete. Required changes to biodiversity-layer.Rmd. Fixed bug in Figure 4 for main text--wrong map selected.

  # Yields. S becomes mean across cultivars, R becomes max of cultivars
  cr2 <- cr[, round(mean(HWAH)), by = .(XNAME, x, y, WTH, PROF, YR)]
  setnames(cr2, c("V1", "PROF"), c("YLDS", "SOL"))
  cr2[, YLDR := cr[, round(max(HWAH)), by = .(XNAME, YR)][, V1]]
  cr2
})
names(ylds) <- crops

>>>>

  # Yields. S becomes mean across cultivars, R becomes max of cultivars
  cr2 <- cr[, round(mean(HWAH)), by = .(XNAME, x, y, WTH, PROF, YR)]
  setnames(cr2, c("V1", "PROF"), c("YLDS", "SOL"))
  cr2[, YLDR := cr[, round(max(HWAH)), by = .(XNAME, YR)][, V1]]
  cr2
})
names(ylds) <- crops
# ylds$maize[, mean(YLDS)]
# ylds$soy[, mean(YLDS)]
# ylds$maize[, unique(WTH)]
# ylds$maize[, unique(SOL)]
